---
title: "<span style='color:#F2F2F2; font-size:100pt'><br>
Example:
</span>"
subtitle: "<span style='color:#DBDBDB; font-size:30pt'>
Subtitle
 </span>"
author: "<span style='color:#DBDBDB; font-size:30pt'>Javier Mtz.-Rdz.</span>"
---

```{r}
#| message: false
#| warning: false
#| include: false
#' To install mytidyfunctions
if (!require("pacman")) install.packages("pacman")
if (!require("mytidyfunctions")) remotes::install_github("JavierMtzRdz/mytidyfunctions")
pacman::p_load(tidyverse, janitor, scales,
               mytidyfunctions, here, extrafont,
               distributional, ggdist)

## Set theme and options ------
set_mytheme(text = element_text(family = "Lato",
                                        size=25),
                    panel.grid = element_blank(),
                    plot.title = formt_text(size = 35))
```


## What is a p-value?

- **Idea:** see if the results were consistent with what random chance might produce.

    1.  Set up a 'null hypothesis' ($H_0$) that they wanted to disprove.
    2.  Assuming that this null hypothesis was in fact true.
    3.  Calculate the chances of getting results at least as extreme as what was actually observed.

## What is a p-value?

> The **p-value** tells us the probability of observing our data, assuming that the null hypothesis is true.

## What is a p-value? 

Suppose we have a <span style='color:#808080'>sample</span> of size $n$.

```{r}

test_statistic <- 0.95
mu1 <- qnorm(test_statistic)


dist_df = tibble(
  dist = c(dist_normal(mu = mu1,sd = 1)),
  dist_name = format(dist)
)

(
  plot0 <- ggplot() +
  stat_dots(data = dist_df,
            aes(xdist = dist),
            n = 500,
            smooth = smooth_discrete(kernel = "ep"),
            alpha = 0.5) + 
    ylab("Count") + 
    xlab(" ") + 
    scale_y_continuous(breaks=NULL) +
    scale_x_continuous(breaks = 0+mu1, 
                       labels = expression(mu),
                       limits = c(mu1-4, mu1+4)) +
    ggtitle(expression(paste(H[0], ": ", mu == mu[0], " vs ",
                             H[1], ": ", mu > mu[0])))
)

  
```

## What is a p-value? {visibility="hidden"}

Based on that, we create our <span style='color:#808080'>null model</span>.

```{r}

q <- map_dbl(c(0.05, 0.025, 0.975, 0.95), qnorm)
z <- tibble(Z = seq(-4, 4, 0.01), density = dnorm(Z)*2.3)

(
  plot <- ggplot(z) + 
    stat_dots(data = dist_df,
            aes(xdist = dist),
            alpha = 0.5) +
    geom_area(aes(Z, density),
              linewidth = 2,
              color = "black",
              fill = "grey",
              alpha = 0.2) + 
    ylab("Density") + 
    xlab(" ") + 
    scale_y_continuous(breaks = NULL) +
    scale_x_continuous(breaks = c(0, mu1), 
                       labels = c(expression(mu[0]),
                                  expression(mu)),
                       limits = c(-4, 4)) +
    ggtitle(expression(paste(H[0], ": ", mu == mu[0], " vs ",
                             H[1], ": ", mu > mu[0]))) 
)
  
```

## What is a p-value? 

Based on that, we create our <span style='color:#808080'>null model</span>.

```{r}

q <- map_dbl(c(0.05, 0.025, 0.975, 0.95), qnorm)
z <- tibble(Z = seq(-4, 4, 0.01), density = dnorm(Z))

(
  plot <- ggplot(z) + 
    geom_area(aes(Z, density),
              linewidth = 2,
              color = "black",
              fill = "grey",
              alpha = 0.2) + 
    ylab("Density") + 
    xlab(" ") + 
    scale_y_continuous(breaks = NULL) +
    scale_x_continuous(breaks = 0, 
                       labels = expression(mu[0]),
                       limits = c(-4, 4)) +
    ggtitle(expression(paste(H[0], ": ", mu == mu[0], " vs ",
                             H[1], ": ", mu > mu[0]))) 
)
  
```



## {fullscreen="true" background-image="frmt/transition.png" background-size="100% 100%"}

<br><br><br><br><br>

::: {style='color:#F2F2F2;font-size:5em;text-align:left;vertical-align:middle' layout="[[1], [-1]]"}
Thanks!
:::

## References

::: {#refs}
:::

